%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Corporate Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Various Corporate Projects} % Project name
    {Full Stack Development, Backend Development, Platform Integration, Team Management} % Role
    {} % Location
    {2014 - 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {HSBC Finance Transformation Platform (2025.02 - Present) Participated in backend development, utilizing tech stacks like Java, Spring, Python, IBM WebSphere, and Copilot.}        
        \item {AI-powered Story Bot: Full stack development using Claude’s API for personalized stories. Technologies: Python, Flask, React, AWS. (May 2024 - Jul. 2024)}
        \item {PayMe from HSBC: Backend development for Auto Top Up feature and cloud migration. Technologies: Java, Spring Cloud, Azure, AWS. (Nov. 2022 - Jul. 2023)}
        \item {DBS Digibank CN: Backend development for mutual funds microservices. Technologies: Java, Spring Cloud, Pivotal Cloud Foundry. (Jul. 2022 - Nov. 2022)}
        \item {DBS Client Connect: Backend development for equity trading microservices. Technologies: Java, Spring Cloud, Pivotal Cloud Foundry. (Dec. 2021 - Jun. 2022)}
        \item {ShowMeBug: Platform integration with Enterprise WeChat, including login and interview entrance. Technologies: Ruby on Rails, PostgreSQL, WeChat SDK. (Jul. 2021 - Sep. 2021)}
        \item {Square Root Inc Projects: Led 50 projects including websites, games, apps, and WeChat mini programs. Responsibilities included team management, contract negotiation, project management, client communications, and software development. (Jan. 2018 - Dec. 2019)}
        \item {Super Brain TV Program WeChat Mini Program: Backend and frontend development for the TV show's WeChat Mini Program. Technologies: Java, Spring, JavaScript, HTML, AliCloud. (Feb. 2018 - Mar. 2018)}
        \item {Chongding Conference: Backend and frontend development for live-streaming trivia app. Technologies: Java, Spring, WebSocket, Netty. (Sep. 2017 - Jan. 2018)}
        \item {Mianbao Live: Backend refactoring for a content monetization platform. Technologies: PHP, TypeScript, Laravel, Go. (Sep. 2017 - Jan. 2018)}
        \item {Fun Live: Full stack development for a knowledge live broadcast platform. Technologies: PHP, JavaScript, HTML, AliCloud, RTMP Streaming. (Jun. 2016 - Sep. 2017)}
        \item {LeanCloud SDK and LeanChat: Development of Objective-C and Java SDKs and their demo app LeanChat. (Jul. 2014 - Oct. 2015)}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
