%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
% Defining the CV entry for the Associate Degree in Computer Application
  \cventry
    {Associate Degree in Computer Application (Ongoing)} % Degree
    {Guangdong University of Foreign Studies} % Institution
    {Guangzhou, China} % Location
    {Oct. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {National Higher Education Self-study Examination. Passed 9 courses: Introduction to Operating Systems, Introduction to Data Structures, Advanced Language Programming (I), English (I), Advanced Mathematics, Database and Applications, Computer Application Technology, Introduction to Law, and Computer Organization and Architecture.}
        \item {Currently preparing for 7 courses: Computer Networks, Basic Electronic Technology (III), Microcomputer and Interface Technology, College Chinese, Mao Zedong Thought and Theory of Socialism with Chinese Characteristics, Ideological and Moral Cultivation and Rule of Law, and Linear Algebra.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Bachelor's in Digital Media Arts (Incomplete)} % Degree
    {Beijing Forestry University} % Institution
    {Beijing, China} % Location
    {Sep. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Completed 13 courses, including Computer Introduction, Fundamentals of Programming, Programming Fundamentals Lab, College English, Advanced Mathematics, Principles and Techniques of Digital Imaging, and Two-Dimensional Graphics Technology.}
        \item {Built a campus assistant Android application Bjfu Assistant, integrating grade checking and alumni forums, with thousands of downloads on campus. Also created an Android app for learning English through movie clips, winning third prize in a hackathon.}
        \item {Ranked top 1 in my school's ACM/ICPC monthly training competition among around 100 top students, including higher-grade peers.}
        \item {Awarded third prize in the "Youth, Health, New Media" digital works creativity contest organized by UNESCO and the Communication University of China for the digital work "Mom Shy To Say."}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Middle School Diploma in Science} % Degree
    {Guangzhou Yuyan Middle School} % Institution
    {Guangzhou, China} % Location
    {Jul. 2007 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Ranked in the top 300 out of 100k students in the Guangzhou High School Entrance exam.}
        \item {Ranked in the top 300 in the 2011 Guangdong NOIP (National Olympiad in Informatics in Provinces).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
