%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
% Defining the CV entry for the Backend Engineer position
  \cventry
    {Backend Engineer} % Job title
    {Meitai Technology Services (Shanghai) Co., Ltd. Guangzhou Branch} % Organization
    {Guangzhou, China} % Location
    {Feb. 2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Backend Engineer outsourced to HSBC Bank under TEKsystems, developing and optimizing backend systems for the \href{https://www.google.com/search?q=Finance+Transformation+Platform+HSBC}{Finance Transformation Platform} in HSBC's Enterprise Technology Department.}
        \item {Maintained features for financial data processing including import, validation, and export, while enhancing submission and approval workflows for new financial headers. Leveraged expertise in accounting, ledger, and banking systems.}
        \item {Managed the full development lifecycle, from local development to UAT testing and production releases. I also troubleshot issues such as deadlocks and IBM Db2 procedures. Copilot was heavily utilized for extensive tasks such as analyzing root causes, generating Python scripts, and documenting around 50 technical guides; some of these guides became key references for teammates facing similar challenges.}
        \item {Worked with technologies such as Java, Spring Boot, IBM Db2, multithreading, Maven, Nexus, Angular, and Python, along with tools including Windows, Control-M, IBM WebSphere Application Server, and Copilot.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelancer} % Job title
    {Self-employed} % Organization
    {Guangzhou, China} % Location
    {Aug. 2023 - Jan. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Analyzed and reimplemented core components of approximately 30 machine learning projects from PyTorch, TensorFlow tutorials, Coursera courses, and open-source repositories. Earned two Coursera certificates: Machine Learning Specialization and Deep Learning Specialization.}
        \item {Prepared for exams to obtain an associate degree, focusing on advanced mathematics, computer organization, and linear algebra. Studied Japanese through immersion in Japanese music and TikTok videos.}
        \item {Contributed as a Full Stack Developer to an AI-powered story bot leveraging Claude's API for personalized storytelling. Implemented prompt configuration and a management interface using Python, Flask, React, and Nginx, with deployment on AWS. Employed Prometheus for monitoring, ELK stack for log management, and ChatGPT-4 for coding support.}
        \item {Maintained a technical blog with 431 original posts at \url{https://lzwjava.github.io}. Utilized large language models for translation into 9 languages, text-to-speech audio, and support for PDF and EPUB formats. Integrated GitHub workflows and used LaTeX for academic papers and resume creation. Technologies included Python, Jekyll, Deepseek, and Mistral.}
        \item {Conducted experiments with llama.cpp, embeddings, rerankers, Retrieval-Augmented Generation, and the MMLU benchmark. Integrated search engine APIs, including Jina AI, Tavily AI Search API, and ElevenLabs API.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Shenzhen Farben Information Technology Co.} % Organization
    {Guangzhou, China} % Location
    {Nov. 2022 - Jul. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Farben is a leading software technology service provider in China. HSBC Bank is one of the largest banking and financial services institutions in the world. \href{https://payme.hsbc.com.hk/}{PayMe} is an HSBC mobile payment service catering to Hong Kong residents.}
        \item {Contracting through Farben, assigned to work for HSBC Bank and contributed to the PayMe project. Participated in the backend development for the Auto Top Up feature, which automatically tops up funds from the user's credit or debit card when their balance falls below a certain amount. Monitored post-payment events from Azure EventHub and checked for top-ups whenever a user set up their auto top-up configuration. Used dedicated object-oriented programming to handle cases elegantly and applied aspect-oriented programming to audit logs for changes in the auto top-up table.}
        \item {Actively contributed to cloud migration following participation in the company's AWS training. Refactored APIs to utilize request header-based routing, ensured secure access and database configurations, and participated in deploying microservices to the new cloud infrastructure.}
        \item {Utilized a strong tech stack including Java, Spring, and Kafka, along with Azure, Azure DevOps, and AWS for cloud services and continuous integration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Engineer} % Job title
    {Beyondsoft Consulting Inc.} % Organization
    {Guangzhou, China} % Location
    {Dec. 2021 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Beyondsoft Consulting is a leading business IT and consulting company. DBS Bank is the largest bank in Southeast Asia by assets and among the largest banks in Asia. Contracting with Beyondsoft, assigned to work for DBS Bank and contributed to DBS Client Connect and DBS DigiBank CN projects.}
        \item {In the DBS Client Connect project, contributed to the development of the equity trading microservice. Responsibilities included creating functionalities for equities display, customer display, pre-trade checks, and placing actual equity trade orders. Integrated Avaloq APIs to enhance the underlying infrastructure and improved the user experience by implementing an edit distance algorithm to refine stock code searches.}
        \item {In the \href{https://www.dbs.com.cn/treasures/digital-service/digibank.html}{DBS DigiBank CN} project, actively contributed to the development of several microservices handling mutual funds management, structured investment products, investment portfolios, and transaction lists. Assisted with performance tests by analyzing logs from Pivotal Cloud Foundry to generate reports on the QPS of the microservices. Developed a tool to automate test generation for the testing tool Karate, streamlining the testing process and improving test coverage.}
        \item {Leveraged cloud technologies and modern frameworks, employing automation best practices with tools such as Java, Spring Cloud, Jira, Confluence, Jenkins, Pivotal Cloud Foundry, and Kibana, and utilizing BDD and TDD methodologies.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
{Freelancer} % Job title
{Self-employed} % Organization
{Guangzhou, China} % Location
{Jan. 2020 - Nov. 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Authored and published technical blogs to share knowledge online, improved English proficiency through engaging with Netflix and literature, and enhanced problem-solving skills by tackling around 500 algorithm problems and participating in Codeforces competitions.}
    \item {Gained a little hands-on experience with big data and cloud-native technologies by exploring introductory tutorials and running examples for Spark, Hadoop, Kubernetes, and Docker.}
    \item {Completed various software projects as a freelancer, including LED Sign Website Development, Enterprise WeChat Integration for ShowMeBug, Web Scraper for Trade Data Collection, and an eBook tool called mathjax2mobi.}
    \item {LED Sign Website Development (lvchensign.com): Developed a website for an LED sign manufacturing company using Bootstrap, HTML, and JavaScript. Implemented features for showcasing products.}
    \item {Enterprise WeChat Integration for ShowMeBug: Contributed to the integration of ShowMeBug with Enterprise WeChat, enabling seamless access to technical interview tools within the Enterprise WeChat ecosystem. Utilized technologies like Ruby, Ruby On Rails, PostgreSQL, and the WeChat SDK to create a smooth user experience for interviewers and candidates.}
    \item {Web Scraper for Trade Data Collection: Developed a web scraper using Python and Selenium to collect trade data for a non-woven fabric company. Automated data extraction and page navigation, processed and stored the data in a SQLite database, and generated reports for business analysis.}
    \item {mathjax2mobi: A tool designed to convert HTML content with MathJax equations into eBook-friendly formats. By transforming LaTeX-based MathJax equations into SVG images, it ensures compatibility with eBook formats like MOBI. Technologies used include Python, BeautifulSoup, and Selenium.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Founder \& Full Stack Engineer} % Job title
{Beijing Square Root Inc.} % Organization
{Beijing, China} % Location
{Jul. 2016 - Dec. 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Beijing Square Root Inc. ran two businesses in 3.5 years. From July 2016 to September 2017, it rolled out and operated Fun Live, a knowledge live broadcast platform. From January 2018 to December 2019, it transformed into a software consulting business.}
    \item {With Fun Live, users could participate in various knowledge lectures such as programming or design. Users could pay fees to attend live sessions or reward lecturers. The lecturer used the OBS tool to push live streams to the server. Users could participate in the lecture in real-time or see the playback later. The platform integrated seamlessly with WeChat for notifications. Hosted around 80 lectures, gained 30,000 users and millions of page views. Responsible for most software development and marketing, leveraging PHP, Vue, HTML, CodeIgniter, MySQL, Redis, LeanCloud, Alibaba Cloud, and WeChat SDK.}
    \item {During the software consulting business period, completed 50 small software projects for customers, including websites, games, and apps. The revenue was around 3 million RMB and the profit was around 700 thousand RMB. Responsible for project negotiation, team management, and some software development. Notable projects are shown below.}
    \item {MianbaoLive: Led a comprehensive backend refactoring effort for MianbaoLive, a one-stop content monetization and social economy platform. Optimized the performance, stability, and user experience of the entire tech stack. Previously used ThinkPHP, Node.js, and Go, and rewrote everything in Laravel for server-side development. The platform included modules for courses, users, content, user attendance, payments, and distribution sales. Partnered with Himalaya, a top audio platform in China, and synchronized content between the platforms.}
    \item {Jiangsu TV's Super Brain Program WeChat Mini Program: Responsible for all backend development and half of the frontend development for the Super Brain program’s WeChat Mini Program. Engaged viewers with interactive puzzle games, enabling them to compete and rank to become the "Super Brain." Used the WeChat Mini Program framework and Wepy (Vue.js) to create game components and ranking pages. Integrated RESTful APIs to fetch game data and user information. Performed extensive performance tuning to ensure the system could handle high concurrency, leveraging caching technologies such as Redis.}
    \item {Chongding Conference: Spearheaded full-stack engineering for Chongding Conference, a mobile trivia app in China resembling HQ Trivia. Designed and implemented services and APIs to handle live trivia events, user management, and real-time question and answer sessions. Utilized Java and Spring for the backend, with Redis and Kafka for caching and message queuing, Zookeeper for service coordination, and Socket.IO for real-time interactions. Developed the admin panel to help operators control the game. The app supported live streaming, real-time interaction, and robust performance under high traffic conditions. Contributed to technical discussions for using SEI (Supplemental Enhancement Information) to synchronize the timestamp of the live streaming with the trivia game interactions.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Cofounder \& Full Stack Engineer} % Job title
{Beijing Dami Entertainment Co.} % Organization
{Beijing, China} % Location
{Nov. 2015 - Jul. 2016} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Beijing Dami Entertainment Co. was a company founded by 6 Internet enthusiasts, including me. Launched and operated the platform CodeReview, a professional platform for code review, communication, and sharing. Gained around 3,000 users.}
    \item {The platform included functionalities such as user management, code submission and review processes, notification systems, payment integration, and event and workshop management. Engineers could submit their code for expert review to improve its quality, and experts received fees for their reviews. The platform also offered workshops and events open to users.}
    \item {Responsible for the development of the backend and half of the frontend. Utilized a strong tech stack including PHP, Vue, CodeIgniter, Alibaba Cloud, and Ping++.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer} % Job title
{Delicious Bookmarks (Beijing) Information Technology Co., Ltd.} % Organization
{Beijing, China} % Location
{Jul. 2014 - Nov. 2015} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Delicious Bookmarks is a leading cloud computing provider in China, known as LeanCloud. It offers a complete set of cloud services including object storage, file storage, web hosting, containers, instant messaging, push notifications, SMS, and game backends. The company serves hundreds of thousands of developer users.}
    \item {Participated in the development of LeanCloud Objective-C SDK and Java SDK. Responsible for the development of LeanChat iOS client and Android client, a chat application designed to demonstrate the instant messaging SDK. Additionally, worked on various frontend projects.}
    \item {Employed a robust tech stack, leveraging modern tools such as iOS SDK, Android SDK, Cocoapods, Xcode, Android Studio, and the Angular framework.}
  \end{cvitems}
}


%---------------------------------------------------------
\end{cventries}
