%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Various Personal Projects} % Project name
    {Open Source Contributions, Blog Development, Backend and Frontend Development, Mobile App Development, Tool Development} % Role
    {} % Location
    {2013 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Algorithm Solutions: Solutions to algorithm problems, hosted on GitHub with 2466 commits, implemented primarily in Java. (2013 - Present)}
        \item {Personal Blog: Maintained a bilingual blog (English and Chinese) with 500 commits, sharing insights on programming, technology, and personal development. (2013 - Present)}
        \item {Live Server: Backend development of a knowledge live broadcast platform using PHP with 660 commits. (2016 - 2017)}
        \item {Live Mobile Web: Developed the mobile frontend of a knowledge live broadcast platform using Vue and JavaScript with 528 commits. (2016 - 2017)}
        \item {Live Web: Developed the desktop frontend of a knowledge live broadcast platform using Vue with 140 commits. (2016 - 2017)}
        \item {Live WeChat Mini Program: Developed the WeChat Mini Program for a knowledge live broadcast platform using JavaScript with 63 commits. (2016 - 2017)}
        \item {Code Review Server: Developed the backend for a professional platform for code review using PHP with 275 commits. (2015 - 2016)}
        \item {Code Review Web: Developed the frontend for a professional platform for code review using Vue and JavaScript with 302 commits. (2015 - 2016)}
        \item {LeanChat iOS: Developed an iOS chat application demonstrating LeanCloud SDK, implemented in Objective-C with 556 commits. (2014 - 2015)}
        \item {LeanChat Android: Developed an Android chat application demonstrating LeanCloud SDK, implemented in Java with 412 commits. (2014 - 2015)}
        \item {Feynman Lectures Mobi: Developed a tool to convert LaTeX to SVG for creating mobi ebooks, implemented in Python with 47 commits. (2020 - 2021)}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
