%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Entrepreneurial Spirit and Product Mindset}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Category
    {} % Role
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {Founded two startups: one with co-founders, and one created by myself. The latter gained 30k users and once achieved revenue of 3 million CNY a year.}
        \item {Secured an investment of around half a million CNY in my startup at 22 years old, and returned it to the investor when shutting down.}
        \item {Applied to Y Combinator twice. One time, entered the second round with around a 3\% acceptance rate, though didn't make it into the batch.}
        \item {Like to initiate new ideas in big companies to actually help the project; tried many ways and created proofs-of-concept in local development in some code branches. Presented them to tech leads to move things forward. Some received good feedback.}
        \item {Gained a lot of social media influencing practice, including blogging, WeChat Subscription channel, TikTok, WeChat Videos, Weibo and LinkedIn. Acquired thousands of followers or 60k page views a year.}
        \item {Used 3 mobile phones and thousands of apps and games to experiment with, including different kinds of apps from tens of countries.}
        \item {As an early user of Blue Sky, I commented on Jeff Dean's first post here and got a like from him; he is Google's Chief Scientist.}
        \item {Own hundreds of small tools and gadgets, such as an Electric/Magnetic Fields meter, etc.}
        \item {If things or products are cheap, very willing to buy different kinds to compare and understand their nuances.}
        \item {Read around 100 books about business, management, and product. Have some connections with people who are experts in these areas.}
        \item {As a crypto and US stock investor since 2018, I took a break due to some losses but resumed investing in 2024, using long-term and regular investing practices. Despite the modest amount, I am pleased to have gained a 25\% profit from NVIDIA after one year of regular investing as of July 2025, as well as a 30\% profit from some of my Bitcoin investments.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}