%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventry}
    {} % Empty Title
    {} % Empty Date/Location
    {} % Empty Type
    {} % Empty Location
    {
        \begin{cvitems}
            \item {Male, born in 1995, Chinese citizen, resides in Guangzhou. Achieved top 300 in Guangdong NOIP 2011 and solved around 1000 algorithm problems online.}
            \item {Studied for one year at Beijing Forestry University before dropping out. Pursuing an associate degree through self-taught education, with nine courses completed.}
            \item {Currently at TEKsystems (outsourced to HSBC Bank). Previous experience includes LeanCloud, Beijing Square Root, Beyondsoft (outsourced to DBS Bank), and Farben Information (outsourced to HSBC Bank).}
            \item {Accumulated 11 years of professional experience, including 8 years in corporate roles and 3 years as a freelancer. Specializes in 2 years of mobile (Android, iOS) engineering, 8 years of full-stack engineering (7 years backend, 1 year frontend), and 1 year in machine learning/big data.}
            \item {Good understanding of HTML, CSS, Browser APIs, JavaScript, Vue.js, React, Angular, and iOS/Android development. Familiar with Java, Spring, Spring Boot, MySQL, Redis, APIs, networking, containers, and distributed systems. Familiar with logging, database, and microservice modules on Alibaba Cloud, AWS, and Azure.}
            \item {Native in Chinese, proficient in English (IELTS 6). Read over 320 books spanning textbooks, personal development, business, technology and history. Read around 2000 comprehensive, long AI answers in the past year.}
            \item {Developed 10 open-source GitHub projects as a main developer, each with over 500 commits available at \href{https://github.com/lzwjava}{https://github.com/lzwjava}. Detailed software portfolio available at \href{https://lzwjava.github.io/pages/portfolio-en}{https://lzwjava.github.io/pages/portfolio-en}.}
            \item {Generous knowledge sharer with AI assistance to help fix grammar, having around 480 original posts on the blog attracting around 60,000 page views a year, and who documents a lot in the corporate environment too.}
            \item {Self-taught researcher with three academic-style papers on reversing myopia and natural vision restoration, inspired by the works of Yin Wang and Todd Becker, backed by three years of experimentation.}
            \item {Engineer with an entrepreneurial spirit and a product mindset, using 3 mobile phones and one thousand of apps and games to play with. Worked as an autonomous AI agent, proficient with extensive AI tools, and becoming better with comprehensive logging and testing.}
            \item {Life hacker in every aspect of life, with thousands of innovative practices—from bringing a second mobile device to help my daughter learn English in China, to using a car vent to dry hair; air fryer lover; has hundreds of small tools or things like a Electric/Magnetic Fields meter, etc.}
            \item {Travel lover and road trip master. Been to the USA twice around age 21, as well as Hong Kong and Macao, and most parts of China. Taken English courses online with 60 Filipino English teachers, and some African or European teachers too.}
        \end{cvitems}        
    }
\end{cventry}